Performance Indicators for Shape and Position Assessment in Electromagnetic Inverse Scattering

### 2025-08-26 paper/main.tex
Authorship update

    \title{Performance Indicators for Shape and Position Assessment in Electromagnetic Inverse Scattering}
    \author{Andr\'e Costa Batista, Ricardo Adriano, and Lucas S. Batista
    \thanks{This work was supported in part by the Brazilian agency CAPES (Coordination for the Improvement of Higher Education Personnel) under Grant 88887.463864/2019-00, the scholarship FAPEMIG-CNPQ (process APQ-06716-24), and CNPq (The National Council for Scientific and Technological Development).}
    \thanks{A. C. Batista, R. Adriano, and L. S. Batista are with the Department of Electrical Engineering, Universidade Federal de Minas Gerais, Belo Horizonte, MG 31270-901, Brazil (e-mail: andre-costa@ufmg.br; rluiz@ufmg.br; lusoba@ufmg.br). A. C. Batista and L. S. Batista are also with Operations Research and Complex Systems Laboratory (ORCS Lab), Belo Horizonte, MG, Brazil.}}

@@

    % \section*{Acknowledgment}

    %     Use the singular heading even if you have many acknowledgments. In most cases, sponsor and financial support acknowledgments are placed in the  unnumbered footnote on the first page, not here.

    %     The authors would like to thank the reviewers for their valuable contributions. This work was supported in part by the Brazilian agencies FAPEMIG, CNPq, and CAPES (Coordination for the Improvement of Higher Education Personnel).

>>>>

    \title{Performance Indicators for Shape and Position Assessment in Electromagnetic Inverse Scattering}
    \author{Andr\'e Costa Batista and Ricardo Adriano
    \thanks{This work was supported in part by the Brazilian agency CAPES (Coordination for the Improvement of Higher Education Personnel) under Grant 88887.463864/2019-00, the scholarship FAPEMIG-CNPQ (process APQ-06716-24), and CNPq (The National Council for Scientific and Technological Development).}
    \thanks{A. C. Batista and R. Adriano are with the Department of Electrical Engineering, Universidade Federal de Minas Gerais, Belo Horizonte, MG 31270-901, Brazil (e-mail: andre-costa@ufmg.br; rluiz@ufmg.br). A. C. Batista is also with Operations Research and Complex Systems Laboratory (ORCS Lab), Belo Horizonte, MG, Brazil.}}

@@

    \section*{Acknowledgment}

    The authors would like to thank Lucas S. Batista for his guidance and manuscript review.
